\scshape Advanced game theory

### 2025-04-16 ch_spm.tex
Add files via upload

	Costly search effort is required to find a trading partner. In particular, each player $i \in I$ chooses effort $a_i \in A_i \coloneqq [0,1]$, and search is successful (so trade occurs) with probability $a_1 a_2 \in [0,1]$. (Thus expected GDP is $2 a_1 a_2$.) We assume that the cost of effort $a_i \in [0,1]$ is $\left( k a_i / \theta + a_i^2/2 \right) / (1+k)$, where $\theta \in \Theta \coloneqq (0,1)$ and $k \in [0,\infty)$. Thus the payoff of player $i \in I$ is
	%
	\begin{equation*}
		u_i^\theta(a_i,a_{-i})
		\coloneqq a_i a_{-i}
		- \frac{ k a_i / \theta + a_i^2/2 }{1+k}
		\quad \text{for all $(a_i,a_{-i}) \in [0,1]^2$.}
	\end{equation*}

>>>>

	Costly search effort is required to find a trading partner. In particular, each player $i \in I$ chooses effort $a_i \in A_i \coloneqq [0,1]$, and search is successful (so trade occurs) with probability $a_1 a_2 \in [0,1]$. (Thus expected GDP is $2 a_1 a_2$.) We assume that the cost of effort $a_i \in [0,1]$ is $\left( k a_i / \theta + a_i^2/2 \right) / (1+k)$, where $\theta \in \Theta \coloneqq (1,\infty)$ and $k \in [0,\infty)$. Thus the payoff of player $i \in I$ is
	%
	\begin{equation*}
		u_i^\theta(a_i,a_{-i})
		\coloneqq a_i a_{-i}
		- \frac{ k a_i / \theta + a_i^2/2 }{1+k}
		\quad \text{for all $(a_i,a_{-i}) \in [0,1]^2$.}
	\end{equation*}

### 2025-04-16 ms.tex
Add files via upload

\date{\small This version: 17 March 2025}

@@

These are the notes for the game theory component of the first-year graduate microeconomics sequence at Oxford, which I first taught in winter 2025.
Thanks to Sami Petersen for exceptionally perceptive proofreading, and to Matteo Escudé, Alexis Ghersengorin, Sanjari Kalantri, Malayvardhan Prajapati, Augustus Smith, Alex Teytelboym, Runhuan Wang and Sally Yang for comments.

@@

A \emph{perfect Bayesian equilibrium (PBE)} is a weak PBE that satisfies natural additional restrictions on $\mu$ even at some off-path information sets $S \in \mathcal{S}$. First, Bayes's rule on the path is strengthened to \emph{Bayes's rule wherever possible,} to cover cases in which it is clear that Bayes's rule could be used at an off-path information set.%
	\footnote{In the example mentioned in \cref{footnote:wpbe_spne}, it is clear that when Bayes's rule is required also at the off-path information set, sequential rationality implies subgame-perfection.}
Secondly, for games with three or more players, a requirement called \emph{no signalling what you don't know} is added, which requires that a deviation (taking us off the path) by player~$i$ should not change the belief of player~$j$ about player~$k$ if $i \neq j \neq k \neq i$.
Formally defining PBE is a little thorny; the original definition \parencite{FudenbergTirole1991} is for a particular class of games. A practical and more generally applicable definition may be found in \textcite{Watson2017}.

>>>>

\date{\small This version: 16 April 2025}

@@

These are the notes for the game theory component of the first-year graduate microeconomics sequence at Oxford, which I first taught in winter 2025.
Thanks to Sami Petersen for exceptionally perceptive proofreading, and to Matteo Escudé, Alexis Ghersengorin, Vishnu Gorthi, Sanjari Kalantri, Malayvardhan Prajapati, Augustus Smith, Alex Teytelboym, Runhuan Wang and Sally Yang for comments.

@@

A \emph{perfect Bayesian equilibrium (PBE)} is a weak PBE that satisfies natural additional restrictions on $\mu$ even at some off-path information sets $S \in \mathcal{S}$. First, Bayes's rule on the path is strengthened to \emph{Bayes's rule wherever possible,} to cover cases in which it is clear that Bayes's rule could be used at an off-path information set.%
	\footnote{In the example mentioned in \cref{footnote:wpbe_spne}, it is clear that when Bayes's rule is required also at the off-path information set, sequential rationality implies subgame-perfection.}
Secondly, for games with three or more players, a requirement called \emph{no signalling what you don't know} is added, which requires that a deviation (taking us off the path) by player~$i$ should not change the belief of player~$j$ about player~$k$ if $i \neq j \neq k \neq i$.
Formally defining PBE is a little thorny; the original definition \parencite{FudenbergTirole1991} is for a particular class of games. A practical and more generally applicable definition may be found in \textcite{Watson2025}.
